### 2016-04-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated west test descriptions in gas burner report

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table). Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.

@@

\section{West Structure Tests}
\label{sec:west_procedure}
Two different test series---Series 22 and Series 24---were conducted in the West Structure. Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure. Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened. Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure. Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} include a schematic and additional details about the procedures used for the experiments during Series 22 and 24.

>>>>

\section{East Structure Tests}
\label{sec:east_procedure}
Five different tests---Tests 2, 3, 4, 5, and 6---were conducted in the East Structure. Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4. The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively. Tests~5 and 6 involved performing a specific set of events three times sequentially. To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table). Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.

@@

\section{West Structure Tests}
\label{sec:west_procedure}
Four different tests---Tests~22, 23, 24, and 25---were conducted in the West Structure. Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
